---
title: "Joining datasets"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Let's practice with different types of joins.

You have two tables, the first table contains all people admitted to a local hospital in the last 100 days with a stroke, and a second table which contains all people admitted to a local hospital in the last 100 days with a heart attack. 

```{r}
# let's build our toy datasets
library(dplyr)

stroke_patients <- data.frame(
  patientID = 1001 + sort(sample(1:40,20)),
  admission_date = Sys.Date() - sample(1:100, 20)
)

heart_patients <- data.frame(
  patientID = 1001 + sort(sample(1:40,20)),
  admission_date = Sys.Date() - sample(1:100, 20)
)
  
```
What will we get if we do a left join?

```{r}
leftjoin_dataset <- left_join(stroke_patients, heart_patients, 
                              by = "patientID",
                              suffix = c(".stroke", ".heart"))

head(leftjoin_dataset)
```
What about an inner join?

```{r}
innerjoin_dataset <- inner_join(stroke_patients, heart_patients, 
                              by = "patientID",
                              suffix = c(".stroke", ".heart"))

head(innerjoin_dataset)
```
If you wanted to produce a table that shows those who have had either a stroke, heart attack, or both, what type of join would you use?

```{r}
# Add your code here!
```

